### 2018-06-22 dissertation/2-complexnetworks/chapter2.tex
updated chapter 2

>>>>

Trust can be hard to define in the context of biological networks, as these networks are often formed by members who have no distinctive properties to categorize as trustworthy or not and, when such properties do exist, the network is probably closer to a social network than a biological one.
The same applies to information networks, which are formed by pieces of data that do not need to maintain active relationships with each other.
Again, an information network that requires trust is likely closer to the category of technological networks.
